Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory

### 2018-10-05 submission/Langmuir/20171017/latex_files/writing/manuscript_revised.tex
Final submission to Langmuir

% Created 2017-08-07 Mon 15:10
% Intended LaTeX compiler: pdflatex
\documentclass[journal=ancac3,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer}
\date{}
\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
\begin{document}

\begin{tocentry}
\includegraphics[width=9cm]{../img/TOC.pdf}
\end{tocentry}

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials
  interfaces enables new technological opportunities in functional
  surfaces and molecular epitaxy.  Understanding the wettability of 2D
  materials represents the crucial first step towards quantifying the
  interplay between the interfacial forces and electric potential of
  2D materials interfaces.  Here we develop the first theoretical
  framework to model the wettability of the doped 2D materials by
  properly bridging the multiscale physical phenomena at the 2D
  interfaces, including: (i) the change of 2D materials surface energy
  (atomistic scale, several \AA), (ii) the molecular reorientation of
  liquid molecules adjacent to the interface (molecular scale,
  \(10^{0} \sim 10^{1}\) nm), and (iii) the electrical double layer
  (EDL) formed in the liquid phase (mesoscopic scales,
  \(10^{0} \sim 10^{4}\) nm).  The latter two effects are found to
  be the major mechanisms responsible for the contact angle change
  upon doping.  When the doping level is electrostatically tuned, we
  demonstrate that 2D materials with high quantum capacitances (e.g.,
  transition metal dichalcogenides, TMDCs) possess a wider range of
  tunability in the interfacial tension.  Furthermore, practical
  considerations such as defects and airborne contamination are also
  quantitatively discussed.  Our analysis implies that the doping
  level can be another variable to modulate the wettability at 2D
  materials interfaces, as well as the molecular packing behavior on a
  2D material-coated surface, essentially facilitating the interfacial
  engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\section{Results and Discussions}
\label{sec:orga11172d}

@@

Figure \ref{fig:dgamma-sigma} presents the calculated \(\Delta
\gamma_{\mathrm{2D}}\) as a function of \(\sigma_{\mathrm{2D}}\) for the
2D materials considered here. Clearly, the doping of 2D materials
reduces their surface energy, or based on the classical definition,
the work required to separate two stacked monolayers is lowered. Among
the 2D materials, we find that graphene shows the highest degree of
surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or \textasciitilde{}20\%
reduction of its intrinsic surface tension \cite{shih_wetting_2013}, at
\(\sigma_{\mathrm{2D}}\) = \(\pm 4\times10^{13}\ e\cdot
\mathrm{cm}^{-2}\). However, as will be discussed later, it does not
imply a reduced wettability because the quantum capacitance effect
also reduces the interfacial tension, \(\gamma_{\mathrm{2D-L}}\). A
clear trend is that the surface energy decrease is more significant in
the 2D semimetals (e.g. graphene, silicene, and germanene) than that
in the 2D semiconductors (e.g. TMDCs). This reflects the fact that the
effective mass of carriers in the 2D semiconductors is much higher
than that in the 2D semimetals \cite{davies_two-dimensional_1997},
thereby resulting in high DOS, as well as a high \(C_{\mathrm{2D}}\)
(see eq \ref{eqn-delta-gamma-sigma-free-2D}). This concept also explains
why the surface energy decrease for silicene and germanene are lower
than that for graphene \cite{Yan_2013}.  To our knowledge, the
doping-induced surface energy change in 2D materials has never been
investigated experimentally, which may be of interest for future
study, inspired by the recent advances in direct measurement of 2D
material surface energy \cite{van_Engers_2017_direct_surf_gr}.

@@

In order to precisely determine the interfacial interactions using MD
simulations, instead of the commonly used model that compared the
nanoscale contact angle by placing a nanodroplet onto a sheet of
suspended 2D material
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
we simulate the difference of the total potential energy, \(E\), between
two separate systems that contain (i) only water molecules with two
surfaces exposing to vacuum (L), and (ii) the same amount of water
molecules with one surface in contact with graphene (placed at z = 0)
and the other surface exposing to vacuum (GL) (see Figure
\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)). Periodic boundary
conditions are used in all three directions of the simulation boxes in
both systems. Additionally, a vacuum layer of 3 nm thick along the
\emph{z}-axis is placed to separate the periodic images of the
graphene-water system. The total energy in both systems can be
formulated as: \(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
2\gamma_{\mathrm{L}}S\) and
\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}} +
\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively, where
\(\mu_{\mathrm{L}}\) is the chemical potential per water molecule in the
bulk phase, \(n_{\mathrm{L}}\) is the number of liquid molecules in the
simulation box, and \(S\) is the area of the \emph{xy}-plane.  A simulation
box with a sufficiently large length of 21 nm in the \emph{z}-direction is used,
with a 18-nm thick block of water molecules, to minimize the effect of
the long-range electrostatic interaction between the charged graphene
and the water molecules at the water-vacuum interface, by ensuring
that the time-averaged dipole moment for the water molecules at the
water-vacuum interface approaches zero (see Supporting Information
Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
(\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}} - \gamma_{L})S =
(\Phi + 2 \gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial
energy, which is defined as \(\Phi = \gamma_{\mathrm{2D-L}} -
\gamma_{\mathrm{2D}} - \gamma_{\mathrm{L}}\), and combining with eq
\ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
\(\Delta \Phi\) can be formulated as:
\begin{equation}
\label{eqn-Delta-Phi-Delta-cos}
\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S - 2\Delta \gamma_{\mathrm{2D}} = -\gamma_{\mathrm{L}} (\Delta \cos \theta)^{\mathrm{Orien}}
\end{equation}
where \((\Delta\cos \theta)^{\mathrm{Orien}}\) corresponds to the
contact angle change due to the reorientation effect. Note that in the
current MD simulation setup, the surface tension of the 2D material
remains unchanged (i.e. \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
Fermi level change with
respect to \(\sigma_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm. In all simulations we assume a
constant surface tension of water \(\gamma_{\mathrm{L}}=72.8\
\mathrm{mJ}\cdot \mathrm{m}^{-2}\). Accordingly, \(\Delta \Phi\) follows
\(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where \(\Delta
\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) correspond to
the change for the vdW and Coulombic interaction potentials,
respectively.

@@

@@

Consider the interface formed between graphene and an (1:1) aqueous
solution, using the parameters of \(d_{\mathrm{H}}=3\) Å
\cite{mcclendon_thickness_1927}, and \(\gamma_{\mathrm{L}}=72.8\
\mathrm{mJ}\cdot \mathrm{m}^{-2}\) at \(T=298\) K, the calculated
\((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
\(\sigma_{\mathrm{2D}}\) is shown in Figure \ref{fig:res-EDL}(b).  Note
that \(c_{0}=10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\) corresponds to the
pure water system. We find that the contact angle change is stronger
in a more diluted electrolyte solution, resulting from an increase in
Debye screening length \(\lambda_{\mathrm{D}}\), which in turn decreases
both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This is distinct from
the that in the typical electrowetting experiment on a dielectric
layer, in which \(C_{\mathrm{YL}}\) is governed by the capacitance of
the dielectric layer, so the contact angle change is almost
independent of the electrolyte concentration
\cite{Mugele_2005}. Moreover, within the range of \(\sigma_{\mathrm{2D}}\)
considered here (\(-4\times10^{13}\) \textasciitilde{} \(4\times10^{13}\ e\cdot
\mathrm{cm}^{-2}\)), the calculated \((\Delta \cos
\theta)^{\mathrm{EDL}}\) is always less than 0.06.  In combination with
the \(\Delta \gamma^{\mathrm{Orien}}_{\mathrm{2D-L}}\) (equivalent to
\(\Delta \Phi\), see previous section) calculated by the MD simulations,
the total change of contact angle \((\Delta \cos
\theta)^{\mathrm{Orien + EDL}}\) due to the doping effect is shown in
Figure \ref{fig:res-EDL}(c). We separately fit the \(\Delta
\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) from the
reorientation effect as functions of \(\sigma_{\mathrm{2D}}\) in n- and
p-doped regimes, respectively (see Figure S5), and use the fitting
results to construct the \(\Delta \Phi-\sigma_{\mathrm{2D}}\)
relation. We find that the reorientation effect is more predominant
than the EDL effect, therefore the overall change of contact angle is
less dependent on the solute concentration, compared with Figure
\ref{fig:res-EDL}(b).

@@

Figures \ref{fig:f-nc-exp}(a) and \ref{fig:f-nc-exp}(b) illustrate how an
 electric field, either from the dopants on the substrate surface or
 from the electrostatic gating, penetrate through a void in a 2D
 material sheet and interact with the liquid phase directly. As a
 result, the EDL is built up adjacent to the substrate surface, with
 the surface excess \(\sigma_{\mathrm{v}}\) and the effective
 capacitance \(C_{\mathrm{v}}\).  Since \(\sigma_{v}\) is equivalent to
 \(\sigma_{\mathrm{2D}}\), together with the EDL and the reorientation
 effects discussed earlier, the modified YLE considering a 2D material
 with voids follows:
\begin{equation}
\label{eqn-def-Delta-cos-mixture}
\Delta \cos \theta = -f\frac{\sigma_{\mathrm{2D}}^{2}}{\gamma_{\mathrm{L}} C_{\mathrm{v}}} 
                     + (1-f)[(\Delta \cos \theta)^{\mathrm{Orien}} + (\Delta \cos \theta)^{\mathrm{EDL}}]
\end{equation}
where \(f\) is the void (defect) fraction in the 2D material. For the
electrostatic gating experiments (see Figure
\ref{fig:f-nc-exp}(a)), the 2D material quantum capacitor
and the dielectric  capacitor are connected in
series, so that the voltage applied between the gate electrode and
2D material, \(V_{\mathrm{G}}\), is given by \cite{tian_multiscale_2016}:
\begin{equation}
\label{eqn-VG-gating}
V_{\mathrm{G}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{0}}}{C_{\mathrm{d}}}
                  + \int_{\sigma_{0}}^{\sigma_{\mathrm{2D}}} \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
\end{equation}
where \(C_{\mathrm{d}}\) is the capacitance of the dielectric layer, and
\(\sigma_{0}\) is the initial doping density of the 2D material,
corresponding to \(V_{\mathrm{G}}=0\).

@@

@@

Here we demonstrate such phenomenon by considering an electrowetting
setup comprised of a thin, high-\(k\) dielectric layer (2 nm HfO\(_{\text{2}}\)
layer with the relative permittivity \(\epsilon_{\mathrm{d}}=24.0\))
underlying a layer of monolayer 2D material (Figure
\ref{fig:dcos-all-2D}(a)).  As addressed earlier, due to the fact that
\((\Delta \cos \theta)^{\mathrm{Orien}}\) of graphene-water system may
not be readily applied to other 2D materials, we compare the
calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
\(V_{\mathrm{G}}\), by using the DFT-calculated \(C_{\mathrm{2D}} -
\sigma_{\mathrm{2D}}\) relations for a variety of 2D materials, as
shown in \ref{fig:dcos-all-2D}(b). Clearly, as a consequence of the high
quantum capacitance, the wettability of the 2D semiconductors
considered is more tunable compared to that for the 2D semimetals. In
other words, in a 2D semiconductor, the value required to reach a
certain is lowered. We predict that the contact angle change \(\Delta \cos \theta\) for
the 2D semiconductors (e.g. TMDCs) can reach up to 0.22\textasciitilde{}0.25 within the range of
\(V_{\mathrm{G}}\) considered, corresponding to an interfacial tension change of 15\textasciitilde{}18 \(\mathrm{mJ} \cdot \mathrm{m}^{-2}\). The analysis presented here suggests that the manipulation of a liquid
droplet on a layer of 2D material doped by an electric displacement field may be feasible
\cite{Mugele_2005,Hayes_2003_nature_EWOD}.

@@

\section{Conclusion}
\label{sec:org0fb53ec}

@@

\newpage{}
\section{Figures}
\label{sec:org764e67e}

>>>>

% Created 2017-08-07 Mon 15:10
% Intended LaTeX compiler: pdflatex
\documentclass[journal=langd5,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
\usepackage{graphicx}
\setkeys{acs}{maxauthors = 0}   %no truncation
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage[section]{placeins}  %enable section number
\SectionNumbersOn
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer}
\date{}
\title{Doping-Driven Wettability of Two-Dimensional Materials: a Multiscale Theory}
\begin{document}

\begin{tocentry}
\includegraphics[width=8.6cm]{../img/TOC_Langmuir.pdf}
\end{tocentry}

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials
  interfaces enables new technological opportunities in functional
  surfaces and molecular epitaxy.  Understanding the wettability of 2D
  materials represents the crucial first step towards quantifying the
  interplay between the interfacial forces and electric potential of
  2D materials interfaces.  Here we develop the first theoretical
  framework to model the wettability of the doped 2D materials by
  properly bridging the multiscale physical phenomena at the 2D
  interfaces, including: (i) the change of 2D materials surface energy
  (atomistic scale, several \AA), (ii) the molecular reorientation of
  liquid molecules adjacent to the interface (molecular scale,
  \(10^{0} \sim 10^{1}\) nm), and (iii) the electrical double layer
  (EDL) formed in the liquid phase (mesoscopic scales,
  \(10^{0} \sim 10^{4}\) nm).  The latter two effects are found to be
  the major mechanisms responsible for the contact angle change upon
  doping, while the surface energy change of a pure 2D material has no
  net effect on the wetting property.  When the doping level is
  electrostatically tuned, we demonstrate that 2D materials with high
  quantum capacitances (e.g., transition metal dichalcogenides, TMDCs)
  possess a wider range of tunability in the interfacial tension,
  under the same applied gate voltage.  Furthermore, practical
  considerations such as defects and airborne contamination are also
  quantitatively discussed.  Our analysis implies that the doping
  level can be another variable to modulate the wettability at 2D
  materials interfaces, as well as the molecular packing behavior on a
  2D material-coated surface, essentially facilitating the interfacial
  engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{../img/scheme-methods.pdf}
\caption{\label{fig:scheme-method} Scheme of the proposed multiscale
  approach for modeling the doping-induced wettability tuning of 2D
  materials. Multiscale phenomena are considered (right side, from top
  to bottom): (i) change of 2D material surface energy
  \(\Delta \gamma_{\mathrm{2D}}\) caused by quantum capacitance, at
  the atomistic scale (several \AA{}). (ii) change of interfacial
  energy by reorientation of interfacial liquid molecules
  \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{Orien}}\), at molecular
  scale (10\(^{\text{0}}\) \textasciitilde{} 10\(^{\text{1}}\)
  nm). (iii) change of interfacial energy as a result of electric
  double layer \(\Delta \gamma_{\mathrm{2D-L}} ^{\mathrm{EDL}}\),
  described by a continuum model (10\(^{\text{0}}\) \textasciitilde{}
  10\(^{\text{4}}\) nm)}
\end{figure}

\section{Results and Discussion}
\label{sec:orga11172d}

@@

Figure \ref{fig:dgamma-sigma} presents the calculated
\(\Delta \gamma_{\mathrm{2D}}\) as a function of
\(\sigma_{\mathrm{2D}}\) for the 2D materials considered
here. Clearly, the doping of 2D materials reduces their surface
energy, or based on the classical definition, the work required to
separate two stacked monolayers is lowered. Among the 2D materials at
the same doping level, we find that graphene shows the highest degree
of surface energy decrease, up to -16 mJ\(\cdot \mathrm{m}^{-2}\) , or
\textasciitilde{}20\% reduction of its intrinsic surface tension
\cite{shih_wetting_2013}, at \(\sigma_{\mathrm{2D}}\) =
\(\pm 4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\).  A clear trend is
that the surface energy decrease is more significant in the 2D
semimetals (e.g. graphene, silicene, and germanene) than that in the
2D semiconductors (e.g. TMDCs). This reflects the fact that the
effective mass of carriers in the 2D semiconductors is much higher
than that in the 2D semimetals \cite{davies_two-dimensional_1997},
thereby resulting in high DOS, as well as a high \(C_{\mathrm{2D}}\)
(see eq \ref{eqn-delta-gamma-sigma-free-2D}). This concept also
explains why the surface energy decrease for silicene and germanene
are lower than that for graphene \cite{Yan_2013}.  To our knowledge,
the doping-induced surface energy change in 2D materials has never
been investigated experimentally, which may be of interest for future
study, inspired by the recent advances in direct measurement of 2D
material surface energy \cite{van_Engers_2017_direct_surf_gr}. Note
that for modeling the macroscopic wetting behavior on a doped 2D
material interface, the reorientation and EDL effects also need to be
taken into account.  As will be discussed later, the doped-induced
change of \(\gamma_{\mathrm{2D}}\) does not imply a reduced
wettability, because the quantum capacitance effect also reduces the
interfacial tension, \(\gamma_{\mathrm{2D-L}}\), which yields zero net
effect on wettability.

@@

In order to precisely determine the interfacial interactions using MD
simulations, instead of the commonly used model that compared the
nanoscale contact angle by placing a nanodroplet onto a sheet of
suspended 2D material
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
we simulate the difference of the total potential energy, \(E\),
between two separate systems that contain (i) only water molecules
with two surfaces exposing to vacuum (L), and (ii) the same amount of
water molecules with one surface in contact with graphene (placed at z
= 0) and the other surface exposing to vacuum (GL) (see Figure
\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)). Note that the current
model can only reveal the static and macroscopic wetting behavior,
while the effects of dynamic properties or surface roughness, as
discussed by some recent MD-based nano-electrowetting studies
\cite{Yuan_2010_PF,Zhao_2015_pillar}, are not considered here.
Periodic boundary conditions are used in all three directions of the
simulation boxes in both systems. Additionally, a vacuum layer of 3 nm
thick along the \emph{z}-axis is placed to separate the periodic
images of the graphene-water system. The total energy in both systems
can be formulated as:
\(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
2\gamma_{\mathrm{L}}S\) and
\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}}
+ \gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively,
where \(\mu_{\mathrm{L}}\) is the chemical potential per water
molecule in the bulk phase, \(n_{\mathrm{L}}\) is the number of liquid
molecules in the simulation box, and \(S\) is the area of the
\emph{xy}-plane.  A simulation box with a sufficiently large length of
21 nm in the \emph{z}-direction is used, with a 18-nm thick block of
water molecules, to minimize the effect of the long-range
electrostatic interaction between the charged graphene and the water
molecules at the water-vacuum interface, by ensuring that the
time-averaged dipole moment for the water molecules at the
water-vacuum interface approaches zero (see Supporting Information
Figure S1).  One can show that
\(E_{\mathrm{GL}} - E_{\mathrm{L}} = (\gamma_{\mathrm{2D-L}} +
\gamma_{\mathrm{2D}} - \gamma_{L})S = (\Phi + 2
\gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial energy,
which is defined as
\(\Phi = \gamma_{\mathrm{2D-L}} - \gamma_{\mathrm{2D}} -
\gamma_{\mathrm{L}}\), and combining with eq
\ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
\(\Delta \Phi\) can be formulated as:
\begin{equation}
\label{eqn-Delta-Phi-Delta-cos}
\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S - 2\Delta \gamma_{\mathrm{2D}} = -\gamma_{\mathrm{L}} (\Delta \cos \theta)^{\mathrm{Orien}}
\end{equation}
where \((\Delta\cos \theta)^{\mathrm{Orien}}\) corresponds to the
contact angle change due to the reorientation effect. Note that in the
current MD simulation setup, the surface tension of the 2D material
remains unchanged (i.e.  \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
Fermi level change with respect to \(\sigma_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm.
When analyzing the reorientation effect on the MD level, we adopt the
water surface tension value of
\(\gamma_{\mathrm{L}}=63.6\ \mathrm{mJ}\cdot \mathrm{m}^{-2}\) in the
SPC/E model \cite{Vega_2007}. Note that the value of
\(\gamma_{\mathrm{L}}\) only affects the results of
\(\Delta \cos \theta\) while not the interaction potential \(\Phi\), as revealed by eq
\ref{eqn-Delta-Phi-Delta-cos}. Moreover, even though the surface
tension from SPC/E model is ~12.6\% lower than the real value (72.8
mJ\(\cdot\)m\(^2\)), such minor difference may not affect our
conclusion. Accordingly, \(\Delta \Phi\) follows
\(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where
\(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\)
correspond to the change for the vdW and Coulombic interaction
potentials, respectively.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.5\linewidth]{../img/2d-ph-dependency+MD.pdf}
\caption{\label{fig:res-EDL} The continuum model: (a) Scheme of the
  interface between the 2D material and the aqueous phase. (b)
  \((\Delta\cos\theta)^{\mathrm{EDL}}\) as a function of
  \(\sigma_{\mathrm{2D}}\) with varied solute concentrations. The
  concentration \(c_{0}\) varies from \(10^{-1}\) to \(10^{-7}\)
  mol\(\cdot\mathrm{L}^{-1}\) (c) Overall change of contact angle
  \((\Delta \cos \theta)^{\mathrm{Orien+EDL}}\) combining the
  orientation and EDL effects, with varied solute concentrations as in
  (b).}
\end{figure}

@@

Consider the interface formed between graphene and an (1:1) aqueous
solution, using the parameters of \(d_{\mathrm{H}}=3\) Å
\cite{mcclendon_thickness_1927},
% and
% \(\gamma_{\mathrm{L}}=72.8\ \mathrm{mJ}\cdot \mathrm{m}^{-2}\) at
% \(T=298\) K,
the calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function
of \(\sigma_{\mathrm{2D}}\) is shown in Figure \ref{fig:res-EDL}(b).
Moderate electrolyte concentrations \(c_{0}\) between \(10^{-1}\) to
\(10^{-7}\) mol\(\cdot\)L\(^{-1}\) are considered, since the corresponding Debye
screening length will be larger than the effective radius of vdW
interactions (to keep the classical continuum-based EDL model valid), under which decoupling the reorientation and EDL effects is
meaningful. Recent experimental and theoretical studies reveal that
the screening lengths of higher concentrations may increase instead of
exponential decay in classical models
\cite{Smith_2016_screening_length,Lee_2017_screening_length}, which
indicates that the addition of reorientation and EDL effects may still be
valid for higher concentrations, provided an accurate description of
the potential profile in the EDL. Nevertheless to keep our multiscale
model simple and generally applicable, we limit the electrolyte
concentration to the range mentioned above. Note that
\(c_{0}=10^{-7}\) mol\(\cdot \mathrm{L}^{-1}\) corresponds to the pure
water system. We find that the contact angle change is stronger in a
more diluted electrolyte solution, resulting from an increase in Debye
screening length \(\lambda_{\mathrm{D}}\), which in turn decreases
both \(C_{\mathrm{GC}}\) and \(C_{\mathrm{DH}}\). This is distinct
from the that in the typical electrowetting experiment on a dielectric
layer, in which \(C_{\mathrm{YL}}\) is governed by the capacitance of
the dielectric layer, so the contact angle change is almost
independent of the electrolyte concentration
\cite{Mugele_2005}. Moreover, within the range of
\(\sigma_{\mathrm{2D}}\) considered here (\(-4\times10^{13}\)
\textasciitilde{} \(4\times10^{13}\ e\cdot \mathrm{cm}^{-2}\)), the
calculated \((\Delta \cos \theta)^{\mathrm{EDL}}\) is always less than
0.06.  In combination with the
\(\Delta \gamma^{\mathrm{Orien}}_{\mathrm{2D-L}}\) (equivalent to
\(\Delta \Phi\), see previous section) calculated by the MD
simulations, the total change of contact angle
\((\Delta \cos \theta)^{\mathrm{Orien + EDL}}\) due to the doping
effect is shown in Figure \ref{fig:res-EDL}(c). We separately fit the
\(\Delta \Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) from
the reorientation effect as functions of \(\sigma_{\mathrm{2D}}\) in
n- and p-doped regimes, respectively (see Figure S5), and use the
fitting results to construct the \(\Delta \Phi-\sigma_{\mathrm{2D}}\)
relation. Comparing the interactions at different length scales, we
find that the reorientation effect is more predominant than the EDL
effect at moderate electrolyte concentrations, while the shift of the
Fermi level in 2D materials has no net effect on the wetting, due to the
cancellation effect explained previously. Therefore the overall change
of contact angle is less dependent on the solute concentration,
compared with Figure \ref{fig:res-EDL}(b).

@@

Figures \ref{fig:f-nc-exp}(a) and \ref{fig:f-nc-exp}(b) illustrate how
an electric field, either from the dopants on the substrate surface or
from the electrostatic gating, penetrate through a void in a 2D
material sheet and interact with the liquid phase directly. As a
result, the EDL is built up adjacent to the substrate surface, with
the surface excess \(\sigma_{\mathrm{v}}\) and the effective
capacitance \(C_{\mathrm{v}}\).  For molecular doping, the EDL charges
in the void regions are built up by the fixed charges on the substrate
surface, while in the electrostatic doping, the electric field from
the charged 2D material to the gate electrode through the void regions
is responsible for building up the EDL. For both cases, we assume that
\(\sigma_{v}\) is equivalent to \(\sigma_{\mathrm{2D}}\), due to
charge conservation. Together with the EDL and the reorientation
effects discussed earlier, the modified YLE considering a 2D material
with voids follows:
\begin{equation}
\label{eqn-def-Delta-cos-mixture}
\Delta \cos \theta = -f\frac{\sigma_{\mathrm{2D}}^{2}}{\gamma_{\mathrm{L}} C_{\mathrm{v}}} 
                     + (1-f)[(\Delta \cos \theta)^{\mathrm{Orien}} + (\Delta \cos \theta)^{\mathrm{EDL}}]
\end{equation}
where \(f\) is the void (defect) fraction in the 2D material. For the
electrostatic gating experiments (see Figure
\ref{fig:f-nc-exp}(a)), the 2D material quantum capacitor
and the dielectric  capacitor are connected in
series, so that the voltage applied between the gate electrode and
2D material, \(V_{\mathrm{G}}\), is given by \cite{tian_multiscale_2016}:
\begin{equation}
\label{eqn-VG-gating}
V_{\mathrm{G}} = \frac{\sigma_{\mathrm{2D}} - \sigma_{\mathrm{0}}}{C_{\mathrm{d}}}
                  + \int_{\sigma_{0}}^{\sigma_{\mathrm{2D}}} \frac{1}{C_{\mathrm{2D}}} \mathrm{d}\sigma'
\end{equation}
where \(C_{\mathrm{d}}\) is the capacitance of the dielectric layer, and
\(\sigma_{0}\) is the initial doping density of the 2D material,
corresponding to \(V_{\mathrm{G}}=0\).

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.65\linewidth]{../img/dcos-all-2D.pdf}
\caption{\label{fig:dcos-all-2D} Electrostatic tunability of 2D
  material wettability: (a) Schematic illustration of the
  2D-material-based electrowetting device, where the 2D material is
  electostatically doped. (b) \((\Delta\cos\theta)^{\mathrm{EDL}}\) as
  a function of \(V_{\mathrm{G}}\) for selected 2D materials.}
\end{figure}

@@

Here we demonstrate such phenomenon by considering an electrowetting
setup comprised of a thin, high-\(k\) dielectric layer (2 nm
HfO\(_{\text{2}}\) layer with the relative permittivity
\(\epsilon_{\mathrm{d}}=24.0\)) underlying a layer of monolayer 2D
material (Figure \ref{fig:dcos-all-2D}(a)).  As addressed earlier, due
to the fact that \((\Delta \cos \theta)^{\mathrm{Orien}}\) of
graphene-water system may not be readily applied to other 2D
materials, we compare the calculated
\((\Delta \cos \theta)^{\mathrm{EDL}}\) as a function of
\(V_{\mathrm{G}}\), by using the DFT-calculated
\(C_{\mathrm{2D}} - \sigma_{\mathrm{2D}}\) relations for a variety of
2D materials, as shown in \ref{fig:dcos-all-2D}(b). Clearly, as a
consequence of the high quantum capacitance, the wettability of the 2D
semiconductors considered is more tunable compared to that for the 2D
semimetals under same the applied gate voltage. In other words, in a 2D
semiconductor, the value required to reach a certain is lowered. We
predict that the contact angle change \(\Delta \cos \theta\) for the
2D semiconductors (e.g. TMDCs) can reach up to
0.22\textasciitilde{}0.25 within the range of \(V_{\mathrm{G}}\)
considered, corresponding to an interfacial tension change of
15\textasciitilde{}18 \(\mathrm{mJ} \cdot \mathrm{m}^{-2}\). The
analysis presented here suggests that the manipulation of a liquid
droplet on a layer of 2D material doped by an electric displacement
field may be feasible \cite{Mugele_2005,Hayes_2003_nature_EWOD}.

@@

\section{Summary and Conclusions}
\label{sec:org0fb53ec}

@@

\end{document}
